CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-25 paper/ms.tex
interpret a, b c and check the validity of the normalization

@@

Working on it...
I think one possible way is to use the velocities correction for the APOGEE data obtained from the spectrum calibration section. Then the optimized APOGEE spectrum can be represented as:
You should look into the velocities and find a right way to describe them.

@@

>>>>

\subsection{\label{sec:level2} Interpret a, b, c in terms of radial velocity}

%Can you interpret a, b, c in terms of radial velocity? If so, how?
After we obtain a, b and c for these stars, we can calibrate the errors in the radial velocities of the combined spectra for these stars. These combined spectra are stored in Apstar files, which are generated by different individual visits after resampling them onto a common, logarithmically-spaced wavelength scale, and after removing derived radial velocities of each visit. The apStar files also include the individual visit spectra, resampled and shifted to rest wavelength. If we need to use the individual visits before resampling, apVisit files are needed. The velocity calibration information is also in apVisits files. In our experiment, we use the resampled spectrum of each visit in Apstar file.

Consider Relativistic Doppler effect. the redshift factor is defined as z. The radial velocities of the stars are much smaller than c, so we have:

\begin{equation}
z = {{\lambda_0 - \lambda_s} \over \lambda_s} = \sqrt{{1+\beta} \over {1-\beta}} -1 \approx \beta
\end{equation}
Where $\beta ={ v \over c} $. $\lambda_0$ and $\lambda_s$ are the wave lengths measured at the observer and the source.

The APOGEE team determine the radial velocities of the stars by two steps.
\bigskip
\\
1. Estimate the radial velocity of each visit by cross-correlating the visit spectrum against a grid of synthetic spectra.
\\
2. Compare the spectrum of each visit with the combined spectrum and re-derive the radial velocity for each visit iteratively.

After obtaining the velocity, we can use the de-Doppler wavelengths and resample the spectrum onto the final logarithmically-spaced wavelength scale using sinc interpolation. Finally, generate combined spectrum by using spectrum of different visits. The data spectrum we use in experiment 1 to 4 is the combined spectrum and we start to use spectrum of each visit in experiment 5.

The radial velocity is related to parameter a, b and c. First, we need to assume that the inferred spectrum is set at rest, which means the radial velocity of it is zero. Second, we think the radial velocity of the data spectrum is equal to the radial velocity of the optimized spectrum. This is because the optimized spectrum is obtained by fitting to the data spectrum. First, we set the radial velocity to be positive if the star is leaving us. If a=1, b=0 and c=0, the optimized spectrum moves one pixel left from the inferred spectrum, which means the data spectrum should move one pixel right and the radial velocity of the data spectrum is not zero and it has a blue shift. Thus the radial velocity is negative and can be obtained by using (8). It's more convenient to use the logarithmic wavelength.
\begin{equation}
\log_{10}\lambda_0 - \log_{10}\lambda_s = \log_{10}(1+\beta)
\end{equation}

All spectrum in Apstar files are set to the same wavelength scale. The wavelength start at 15100.802 $\AA$ and the logarithmic wavelength grid spacing between two pixels is $6*10^{-6}$. By using (9), we find that one pixel is related to radial velocity 4144.68 m/s, which means if a=1 b= 0 and c=0, the radial velocity deviation in the APOGEE data is $-4144.68 m/s$

Thus we can use a, b and c to determine the radial velocity correction for each visits of the APOGEE data.
\begin{equation}
v_{deviation} = (c-a)*v_{pixel}
\end{equation}
Where $v_{deviation}$ is the deviation of the APOGEE data and $v_{pixel}$ =  4144.68 m/s.

Before we obtain a, b and c for each visit, we need to continuum-normalize the spectrum of each visit. The spectrum for each visit we use are in apstar files, which are already resampled to the sample wavelength scale with 8575 pixels. The method we use is the same as the one in Ness et al 2015. First, cut all 8575 pixels into three chunks: [[371,3192], [3697,5997], [6461,8255]]. Then, do pseudo-normalization in these three regions and obtain the pseudo-normalized flux and inverse variance. Third, put a mask on the spectrum. Finally, fit the continuum spectrum in the continuous regions by using a 3-order sinusoid function and obtain the continuum-normalized spectrum.

To check whether it works, we can infer labels by using these normalized visit. If the inferred labels from each visit are similar, the normalization works. 
The details are in experiment 5.

\subsection{\label{sec:level2} Obtain new information from the individual exposures}

%How do you continuum-normalize the individual exposures, and can you demonstrate to me that your proposal of how to do that is working well?

@@

Working on it...

@@

\subsection{\label{sec:level2}Experiment 5}

Here we choose the four stars with biggest a-c and obtain the radial velocity correction. The spectrum we use are the combined spectrum for these four stars. Then we derive their radial velocities correction and de-Doppler the wavelength. Use Sinc interpolation to resample them onto the same wavelength scale and obtain the calibrated spectrum. The wavelength scale is the same as the one in Apstar file. Finally, plot the data spectrum and the calibrated spectrum in figure 11.

\includegraphics[width=170mm]{figure_11.png}
\bigskip

\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum}
\bigskip

After that, we want to calibrate the spectrum for each visit. Choose the first star in figure 11 and normalize all visits for it. Then, plot them in figure 12. To check whether our normalization works, infer labels for each visit and compare them. If our normalization works, the inferred labels of each visit should be similar to each other.

\includegraphics[width=170mm]{figure_12.png}
\bigskip

\centerline{Fig.12 Comparison of each visit for star XXR}
\bigskip

We also plot the histogram which shows the deviations of the inferred labels for each visits from the ones for combined spectrum. The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum. The data we use is the 614 stars in experiment 1 to 4. If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.

\includegraphics[width=170mm]{figure_13.png}
\bigskip

\centerline{Fig.13 Histogram for the deviations of the inferred labels}
\bigskip

plot the correct radial velocity spetrum by using sinc interpolation
plot the inferred labels plot the normalized spectrum for each apvisit and compare
plot histogram of the deviation for inf labels for each visits.
